Software Clusterings with Vector Semantics and the Call Graph

### 2019-08-12 slides/slides.tex
Clean poster dir

\documentclass{beamer}
\usepackage{algpseudocode}
\renewcommand{\vec}{\mathbf}
\usepackage[utf8]{inputenc}
 \usetheme{Boadilla}
 \usepackage{ragged2e}
\justifying
%Information to be included in the title page:
\title{Software Clusterings with Vector Semantics and the Call Graph}
\author[Marios Papachristou]{Marios Papachristou \\ \small \url{papachristoumarios@gmail.com} \\ \small \url{el15101@mail.ntua.gr}}

@@

\begin{document}

@@

$$\textrm{MoJo} (\mathcal C_1, \mathcal C_2) = \min \{ \textrm{mno} (\mathcal C_1, \mathcal C_2), \textrm{mno}(\mathcal C_2, \mathcal C_1) \}$$
    \item<4-> Exact computation is not \textbf{efficient} so a \t-extbf{heuristic} is proposed.

@@

\begin{itemize}
    \item LIMBO. An Information-Theoretic Clustering Algorithm based on the Agglomerative Information Bottleneck. The initial clusters are put on a B+-tree variant (DCF Tree) and then the leaves of the tree become the input of the Agglomerative Information Bottleneck Algorithm.

    \item ACDC. TODO

@@

\begin{itemize}
    \item Testing our system with various codebases to validate method's generalizability
    \item Development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
    \item Integration with more static analyzers 
\end{itemize}

@@

\begin{frame}{}
  \centering \Large {
  \emph{Thank you!}}
  \texttt{https://github.com/papachristoumarios/sade}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage{algpseudocode}
\renewcommand{\vec}{\mathbf}
\usepackage[utf8]{inputenc}
 \usetheme{Boadilla}
 \usepackage{ragged2e}
\justifying
%Information to be included in the title page:
\title[SADE]{Software Clusterings with Vector Semantics and the Call Graph}
\author[Marios Papachristou]{Marios Papachristou \\ \small \url{papachristoumarios@gmail.com} \\ \small \url{el15101@mail.ntua.gr}}

@@

\usepackage{graphicx}
\begin{document}

@@

$$\textrm{MoJo} (\mathcal C_1, \mathcal C_2) = \min \{ \textrm{mno} (\mathcal C_1, \mathcal C_2), \textrm{mno}(\mathcal C_2, \mathcal C_1) \}$$
    \item<4-> Exact computation is not \textbf{efficient} so a \textbf{heuristic} is proposed.

@@

\begin{itemize}
	\item LIMBO
	\item ACDC

@@

\begin{itemize}
    %\item Testing our system with various codebases to validate method's generalizability
    \item Development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
    \item Integration with more static analyzers 
\end{itemize}

\begin{frame}
\frametitle{Code and Data}

\begin{figure}
\centering
\includegraphics[height=0.4\paperheight]{source_and_paper_qr.png} \qquad
\includegraphics[height=0.4\paperheight]{dataset_qr.png}
\end{figure}

\centering \Large {
  \emph{Thank you!}}
  \url{https://github.com/papachristoumarios/sade}
  \url{https://zenodo.org/record/2652487}

@@
